Check Coverage

### 2020-06-23 analysis/merge_data.Rmd
Calculate BAT metrics in function. Update functions to map over plot_id variable.

First for one study, 311
```{r}
glm_correction <- function(study, plot_num){
  model_data <- fd_table %>% filter(metric == "FRic", study_id == study, plot == plot_num)
  fit <- glm(value ~ richness, data = model_data)

>>>>

First for one study, 311
```{r}

glm_correction <- function(study, plot_num){
  model_data <- fd_table %>% filter(metric == "FRic", study_id == study, plot == plot_num)
  fit <- glm(value ~ richness, data = model_data)
